Bridging Gaps: Investigating COVID-19's Influence on Health Disparities in Connecticut

### 2023-10-31 manuscript/manuscript.tex
update table format

%% preamble: Keep it clean; only include those you need
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
% for space filling
\usepackage{lipsum}
% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

\ref{tab:connecticut-counties}

\begin{table}[h]
    \centering
    \caption{Demographics and Education Levels by County} \label{tab:connecticut-counties}
    \begin{tabular}{l|cccccccc}
    \hline
    \textbf{CATEGORY} & \textbf{Fairfield County} & \textbf{Hartford County} & \textbf{Litchfield County} & \textbf{Middlesex County} & \textbf{New Haven County} & \textbf{New London County} & \textbf{Tolland County} & \textbf{Windham County} \\ \hline
    Total Population & 944977 & 894465.25 & 182657.5 & 163318.25 & 858678 & 268477.75 & 151218.75 & 116608.75 \\
    RACE &  &  &  &  &  &  &  &  \\
    American Indian and Alaska Native race alone & 0.24 & 0.3075 & 0.2025 & 0.195 & 0.1725 & 0.605 & 0.05 & 0.565 \\
    Asian & 5.2925 & 5.2925 & 1.9 & 3.0625 & 4.005 & 4.12 & 4.675 & 1.3675 \\
    Black or African American & 11.405 & 13.7025 & 1.83 & 5.385 & 13.34 & 5.8175 & 3.1075 & 2.33 \\
    Native Hawaiian and Pacific Islander & 0.055 & 0.035 & 0 & 0.005 & 0.0225 & 0.025 & 0 & 0.015 \\
    White & 72.6325 & 70.67 & 92.6025 & 88.0875 & 73.2875 & 80.6175 & 88.025 & 88.8725 \\
    Ethnicity &  &  &  &  &  &  &  &  \\
    Hispanic & 19.53 & 17.8275 & 6.15 & 6.12 & 17.885 & 10.5 & 5.4475 & 11.6375 \\
    Education &  &  &  &  &  &  &  &  \\
    Associates & 20.74 & 25 & 27.9225 & 26.46 & 24.4175 & 29.2675 & 26.315 & 30.9775 \\
    Bachelor & 26.53 & 21.4575 & 20.635 & 23.3325 & 18.785 & 18.3175 & 23.4075 & 14.595 \\
    Graduate Degree & 21.14 & 16.475 & 14.6975 & 18.4525 & 16.3425 & 15.18 & 17.865 & 9.55 \\
    HS Graduate & 21.4725 & 26.7175 & 29.5875 & 26.0275 & 30.565 & 29.46 & 27.03 & 33.5125 \\
    Less than High School & 10.12 & 10.3525 & 7.1575 & 5.7275 & 9.8875 & 7.7725 & 5.385 & 11.365 \\ \hline
    \end{tabular}
    \end{table}

@@

\subsubsection{Median Income}
The disparity in median income across the four years highlights economic fluctuations, with 
2020 exhibiting the highest income levels. County-wise analysis reveals that county 1 has a significantly 
greater median income than other counties. This discrepancy in wealth signifies potential disparities in 
access to resources and opportunities, which can significantly impact health outcomes.

\subsubsection{Housing Affordability}
The stable trend in the percentage of renters spending 50 percent of their income on rent suggests a 
consistent challenge faced by residents across the years. County 1 and 5 facing significantly higher 
rates reflect housing affordability issues, possibly indicating economic strains experienced by residents in these areas.

\subsubsection{Rehospitalization Rates}
The absence of significant differences in rehospitalization rates by both county and year indicates 
a consistent healthcare landscape. However, it's crucial to explore the reasons behind this stability to identify 
potential factors contributing to the overall health system's effectiveness.

\subsubsection{Food Stamps Usage}
Counties 8, 2, and 5 having higher percentages of the population on food stamps imply economic challenges 
faced by residents in these regions. This data aligns with the housing affordability trends, suggesting a potential 
link between financial struggles and reliance on government assistance programs.

\subsubsection{Uninsured Rates}
County 1's consistently high uninsured rate points towards a significant healthcare accessibility issue, 
possibly linked to economic factors impacting insurance affordability. Year 3's (2019) lower uninsured rate signifies 
a positive change; understanding the policies or interventions during this period could offer valuable insights into 
effective healthcare reforms.

>>>>

%% preamble: Keep it clean; only include those you need
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
% for space filling
\usepackage{lipsum}
% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}
\usepackage{tabularx}
\usepackage{adjustbox}

@@

\begin{table}[]
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{lllllllllllllll}
                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  &  \\
  \textbf{County}           &                                              & Fairfield County & Hartford County & Litchfield County & Middlesex County & New Haven County & New London County & Tolland County & Windham County &  &  &  &  &  \\
  \textbf{Total Population} &                                              & 944977           & 894465.25       & 182657.5          & 163318.25        & 858678           & 268477.75         & 151218.75      & 116608.75      &  &  &  &  &  \\
  \textbf{Race}             & American Indian and Alaska Native race alone & 0.24             & 0.3075          & 0.2025            & 0.195            & 0.1725           & 0.605             & 0.05           & 0.565          &  &  &  &  &  \\
                            & Asian                                        & 5.2925           & 5.2925          & 1.9               & 3.0625           & 4.005            & 4.12              & 4.675          & 1.3675         &  &  &  &  &  \\
                            & Black or African American                    & 11.405           & 13.7025         & 1.83              & 5.385            & 13.34            & 5.8175            & 3.1075         & 2.33           &  &  &  &  &  \\
                            & Native Hawaiian and Pacific Islander         & 0.055            & 0.035           & 0                 & 0.005            & 0.0225           & 0.025             & 0              & 0.015          &  &  &  &  &  \\
                            & White                                        & 72.6325          & 70.67           & 92.6025           & 88.0875          & 73.2875          & 80.6175           & 88.025         & 88.8725        &  &  &  &  &  \\
  \textbf{Ethnicity}        & Hispanic                                     & 19.53            & 17.8275         & 6.15              & 6.12             & 17.885           & 10.5              & 5.4475         & 11.6375        &  &  &  &  &  \\
  \textbf{Education}        & Associates                                   & 20.74            & 25              & 27.9225           & 26.46            & 24.4175          & 29.2675           & 26.315         & 30.9775        &  &  &  &  &  \\
                            & Bachelor                                     & 26.53            & 21.4575         & 20.635            & 23.3325          & 18.785           & 18.3175           & 23.4075        & 14.595         &  &  &  &  &  \\
                            & Graduate Degree                              & 21.14            & 16.475          & 14.6975           & 18.4525          & 16.3425          & 15.18             & 17.865         & 9.55           &  &  &  &  &  \\
                            & HS Graduate                                  & 21.4725          & 26.7175         & 29.5875           & 26.0275          & 30.565           & 29.46             & 27.03          & 33.5125        &  &  &  &  &  \\
                            & Less the High School                         & 10.12            & 10.3525         & 7.1575            & 5.7275           & 9.8875           & 7.7725            & 5.385          & 11.365         &  &  &  &  &  \\
                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  & 
  \end{tabular}%
  }
  \end{table}

@@

\subsection{Median Income}
The disparity in median income across the four years highlights economic fluctuations, with 
2020 exhibiting the highest income levels. County-wise analysis reveals that county 1 has a significantly 
greater median income than other counties. This discrepancy in wealth signifies potential disparities in 
access to resources and opportunities, which can significantly impact health outcomes. The stable trend 
in the percentage of renters spending 50 percent of their income on rent suggests a 
consistent challenge faced by residents across the years. County 1 and 5 facing significantly higher 
rates reflect housing affordability issues, possibly indicating economic strains experienced by residents in these areas.
The absence of significant differences in rehospitalization rates by both county and year indicates 
a consistent healthcare landscape over the years prior to the 2020 pandemic.
Counties 8, 2, and 5 having higher percentages of the population on food stamps imply economic challenges 
faced by residents in these regions. This data aligns with the housing affordability trends, suggesting a potential 
link between financial struggles and reliance on government assistance programs.
County 1's significant high uninsured rate points towards a significant healthcare accessibility issue, 
possibly linked to economic factors impacting insurance affordability. Year 3's (2019) lower uninsured rate signifies 
a positive change; understanding the policies or interventions during this period could offer valuable insights into 
effective healthcare reforms.
